Meeting the Challenges of Modeling Astrophysical Thermonuclear Explosions: \castro, \maestro, and the \amrex\ Astrophysics Suite

### 2017-10-14 astronum_2017/astronum-amrex.tex
some more scaling discussion

Figure~\ref{fig:maestro_scaling} shows strong scaling for \maestro\ on the 3-d
XRB problem.  This is a typical \maestro\ application~\cite{xrb3}, where burning
can be a significant part of the overall evolution.  We ran on both
OLCF titan and NERSC edison.  We see that the code scales well to
$\mathcal{O}(10^4)$ processors.  The main limitation to the scaling at
the moment are the multigrid solves used to enforce the projection (in
particular the nodal solver).  \maestro\ also does not yet take
advantage of the tiling capabilities offered in \amrex.  These will be
addressed in the future as we port \maestro\ to the
\cpp\ \amrex\ codebase to take advantage of ongoing development.

Figure~\ref{fig:castro-scaling} shows scaling behavior for a pure
hydro + real EOS problem and a hydro / real EOS, + self-gravity
problem.  All tests were run on OLCF titan.  The AMD processors in
titan can be used in a 8 or 16 cores / node configuration.  For all
these runs, we ran in the 16 cores / node mode.  All runs also used
the PGI 17.7 compilers.  We see excellent scaling behavior for the
pure hydro problem.  For the self-gravity problem, we scale well with
a uniform grid, but with a $4\times$ jump for the AMR level on top of
this, we do worse at higher core counts.  This is a challenging
problem, as only 3\% of the domain volume is refined.  For a given
core count, there are a number of different combinations of MPI ranks
and OpenMP threads we can use.  In general, with multilevel problems,
we found the best performance with fewer MPI ranks and more OpenMP
threads.

>>>>

Figure~\ref{fig:maestro_scaling} shows strong scaling for \maestro\ on
the 3-d XRB problem.  This is a typical
\maestro\ application~\cite{xrb3}, where burning can be a significant
part of the overall evolution.  We ran on both OLCF titan and NERSC
edison.  We see that the code scales well to $\mathcal{O}(10^4)$
processors.  The upturn at the end of the scaling curves on titan
reflect the change from 1 MPI task / 8 OpenMP threads per NUMA node to
1 MPI task / 16 OpenMP threads per compute node (2 NUMA nodes).  The
main limitation to the scaling at the moment are the multigrid solves
used to enforce the projection (in particular the nodal solver).
\maestro\ also does not yet take advantage of the tiling capabilities
offered in \amrex.  These will be addressed in the future as we port
\maestro\ to the \cpp\ \amrex\ codebase to take advantage of ongoing
development.

Figure~\ref{fig:castro-scaling} shows scaling behavior for a pure
hydro + real EOS problem and a hydro / real EOS, + self-gravity
problem.  All tests were run on OLCF titan.  The AMD processors in
titan can be used in an 8 or 16 cores / node configuration.  For all
these runs, we ran in the 16 cores / node mode.  All runs also used
the PGI 17.7 compilers.  We see excellent scaling behavior for the
pure hydro problem.  For the self-gravity problem, we scale well with
a uniform grid, but with a $4\times$ jump for the AMR level on top of
this, we do worse at higher core counts.  This is a challenging
problem, as only 3\% of the domain volume is refined.  For a given
core count, there are a number of different combinations of MPI ranks
and OpenMP threads we can use.  In general, with multilevel problems,
we found the best performance with fewer MPI ranks and more OpenMP
threads.
